%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

%\usepackage{ulem}
\usepackage{setspace}
\usepackage[left=0.9in,top=0.6in,right=0.9in,bottom=0.7in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{ZIYI WU} % Your name
\address{
% 27 King's College Circle
Toronto, Ontario M5S 1A1 Canada
} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{
% (+86) 188 1023 7672 \\ 
\href{mailto:ziyiwu@cs.toronto.edu}{ziyiwu@cs.toronto.edu} \\ 
% \href{mailto:dazitu616@gmail.com}{dazitu616@gmail.com} \\ 
\url{https://wuziyi616.github.io/}}
%https://github.com/Wuziyi616} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\textbf{University of Toronto}}, {Toronto, Canada} \hfill {\em Sept. 2021 -- Present}\\
\textbf{Ph.D.} in Computer Science\\
Advisor: Prof. Animesh Garg \& Prof. Andrea Tagliasacchi


{\textbf{Tsinghua University}}, {Beijing, P.R.China} \hfill {\em Aug. 2017 -- Jun. 2021}\\
\textbf{B.Eng.} in Automation\\
Advisor: Prof. Jiwen Lu


\end{rSection}



\begin{rSection}{Publications \& Manuscripts}

\begin{enumerate}
\item \textbf{Ziyi Wu}$^{*}$, Yueqi Duan$^{*}$, He Wang, Qingnan Fan, Leonidas J. Guibas.\\
\textbf{IF-Defense: 3D Adversarial Point Cloud Defense via Implicit Function based Restoration}\\
Submitted to \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence (T-PAMI)}.
% \href{https://arxiv.org/abs/2010.05272}{[\underline{arXiv}]}


\item Ziwei Wang, Yunsong Wang, \textbf{Ziyi Wu}, Jiwen Lu, Jie Zhou.\\
\textbf{Instance Similarity Learning for Unsupervised Feature Representation}\\
\textit{IEEE International Conference on Computer Vision (ICCV), 2021}.


\item Ziwei Wang, Jiwen Lu, \textbf{Ziyi Wu}, Jie Zhou.\\
\textbf{Learning Efficient Binarized Object Detectors with Information Compression}\\
\textit{IEEE Transactions on Pattern Analysis and Machine Intelligence (T-PAMI), 2021}.


\item Ziwei Wang, \textbf{Ziyi Wu}, Jiwen Lu, Jie Zhou.\\
\textbf{BiDet: An Efficient Binarized Object Detector}\\
\textit{IEEE/CVF Conference on Computer Vision and Pattern Recognition (CVPR), 2020}.
%\href{https://arxiv.org/abs/2003.03961}{[\underline{arXiv}]}


\item Zimeng Tan, Yongjie Duan, \textbf{Ziyi Wu}, Jianjiang Feng, Jie Zhou.\\
\textbf{A Cascade Regression Model for Anatomical Landmark Detection}\\
\textit{Medical Image Computing and Computer Assisted Intervention (MICCAI) Workshop, 2019}.
% \href{https://link.springer.com/chapter/10.1007/978-3-030-39074-7_5}{[\underline{Springer}]}


\item Zhanwei Xu, \textbf{Ziyi Wu}, Jianjiang Feng.\\
\textbf{CFUN: Combining Faster R-CNN and U-net Network for Efficient Whole Heart Segmentation}\\
\textit{arXiv, 2018}
% \href{https://arxiv.org/abs/1812.04914}{[\underline{arXiv}]}
%\newline
\end{enumerate}

\end{rSection}



\begin{rSection}{Experience}

\textbf{SenseTime Ltd.} \hfill {\em Mar. 2021 -- Aug. 2021}\\
{Research Intern} \hfill {Mentor: Dr. Kai Chen \& Wenwei Zhang}\\
Open source codebase for 3D scene understanding (\href{https://github.com/open-mmlab/mmdetection3d}{MMDetection3D})


\textbf{Stanford University} \hfill {\em Jun. 2020 -- Sept. 2020}\\
{Research Intern} \hfill {Supervisor: Prof. Leonidas J. Guibas}\\
3D adversarial attack and defense in point cloud


\textbf{Tsinghua University} \hfill {\em Apr. 2019 -- May. 2020}\\
{Undergraduate Researcher} \hfill {Supervisor: Prof. Jiwen Lu}\\
Efficient design for 2D object detectors

\end{rSection}



\begin{rSection}{Selected Honors}

\begin{itemize}
    \item Outstanding Graduates (Beijing, Tsinghua University \& Dept. of Automation), 2021
    
    \item SenseTime Undergraduate Scholarship for AI Research, 2020
    
    \item Xiaomi Scholarship, Tsinghua University, 2020
    
    \item Fang Chongzhi Scholarship, Tsinghua University, 2019
    
    \item National Scholarship, Tsinghua University, 2018
    
    \item Spark Program Membership, Tsinghua University
    
    \item Innovation Award of Science and Technology, Tsinghua University, 2018-2020
    
    \item Champion of the 20th Electronic Design Competition, Tsinghua University, 2018
\end{itemize}

\end{rSection}

\end{document}
